Supplmentary material - A plot is worth a thousand tests: assessing residual diagnostics with visual inference

### 2023-03-21 paper_comparison/appendix.Rmd
create table for demogrphic

>>>>

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(pronoun) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  rename(Pronoun = pronoun) %>%
  kableExtra::kable(format = "latex", booktabs = TRUE)
```

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(age_group) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  rename(`Age group` = age_group) %>%
  kableExtra::kable(format = "latex", booktabs = TRUE)
```

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(education) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp, values_fill = 0) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  slice(c(2, 1, 3, 4, 5)) %>%
  rename(`Education` = education) %>%
  kableExtra::kable(format = "latex", booktabs = TRUE)
```

```{r}
vi_survey %>%
  mutate(pronoun = ifelse(pronoun == "They", "Other", pronoun)) %>%
  mutate(pronoun = factor(pronoun, levels = c("He", "She", "Other"))) %>%
  group_by(exp, set) %>%
  summarise(across(everything(), first)) %>%
  count(previous_experience) %>%
  mutate(exp = paste("Period", c("I", "II", "III")[exp - 2])) %>%
  pivot_wider(values_from = n, names_from = exp) %>%
  mutate(Total = `Period I` + `Period II` + `Period III`) %>%
  rename(`Previous experience` = previous_experience) %>%
  kableExtra::kable(format = "latex", booktabs = TRUE)
```
